### 2013-03-31 exam6/2.tex
Small corrections.

\begin{verbatim}
"1. NSF Proposal 1218390"
"1.1 Overview"
"1.1.1 WAT?"
"1.1.2 Motivations"
"1.1.2.1 unmotivating"
"1.2 Middle (fell asleep)"
"1.3 Conclusions"
"1.4 Budget"
"1.4.1 very large"
"1.4.2 lots of BU undergrads"
\end{verbatim}

@@

\noindent
Develop the \texttt{sameNote} method, which \texttt{equals} relies on.
(Two notes are equal if they have the same text and subnotes.)

>>>>

\begin{verbatim}
"1. NSF Proposal 1218390"
"1.1. Overview"
"1.1.1. WAT?"
"1.1.2. Motivations"
"1.1.2.1. unmotivating"
"1.2. Middle (fell asleep)"
"1.3. Conclusions"
"1.4. Budget"
"1.4.1. very large"
"1.4.2. lots of BU undergrads"
\end{verbatim}

@@

\noindent
Develop the \texttt{sameNote} method, which \texttt{equals} relies on.
(Two notes are the same if they have the same text and subnotes.)
